\LARGE \bf How Children Perceive and Interact with a Robot that Behaves Unexpectedly -- The Domino Experiment

### 2014-09-16 paper.tex
Added abstract + layout changes

\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction: Towards Sustained Engagement}

@@

\subsection{The Ranger robot}

@@

@@

\begin{table}[h]
\centering
\footnotesize
\begin{tabular}{p{0.9\linewidth}}
    \toprule
    \textbf{Construct \emph{expectations}} \\
    \midrule

>>>>

Presented is a study on the impact of unexpected robot behaviours on the
perception of a robot by children and their subsequent engagement in a playful interaction.
We propose an original analysis methodology which blends behavioural cues and
reported phenomenological perceptions into a compound \emph{index}.

While we found only a limited recognition of the different misbehaviours of the
robot that we attribute to the age of the subject (M=4.46), interesting findings
include a sustained engagement level, an unexpectedly low level of attribution
of higher cognitive abilities and a \emph{negative} correlation between
anthropomorphic projections and actual behavioural engagement.

Besides, this study operationalizes for the first time the
\emph{anthropomorphism index} proposed by~\cite{fink2014dynamics}, which proves a
valuable tool to assess qualitative psycho-behavioural episodes occurring during
human-robot interaction.

\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\subsection{Towards Sustained Engagement}

@@

@@

\subsubsection{The Ranger robot}

@@

\begin{table}[h!t]
\centering
\footnotesize
\begin{tabular}{p{0.9\linewidth}}
    \toprule
    \textbf{Construct \emph{expectations}} \\
    \midrule
